Federated Learning's Blessing:\\ FedAvg has Linear Speedup

### 2020-09-17 source-iclr/app_sumarization.tex
proof th1 minor
svx appendix

\begin{table}[h!]
\hspace{-4em}
{
\centering
\tiny
\begin{tabular}{|c|c|c|c|c|c|c|c|}
\hline Reference                 & Convergence rate    & E                           			& NonIID & Participation & Extra Assumptions  		  & Setting  \\ \hline\hline 
FedAvg\cite{li2019convergence}         & $\cO(\frac{E^2}{T})$& $\cO(1)$                    		& \cmark & Partial       & Bounded gradient   		  & Strongly convex  \\ \hline
FedAvg\cite{haddadpour2019convergence} & $\cO(\frac{1}{KT})$ & $\cO(K^{-1/3}T^{2/3})^{\dagger}$ & \cmark$^{\ddagger\ddagger}$ & Partial       & Bounded gradient diversity   & Strongly convex$^{\mathsection}$  \\ \hline
FedAvg\cite{koloskova2020unified} & $\cO(\frac{1}{NT})$ & $\cO(N^{-1/2}T^{1/2})$     	& \cmark & Full       & Bounded gradient   & Strongly convex  \\ \hline
FedAvg\cite{karimireddy2019scaffold} & $\cO(\frac{1}{NT})^{\dagger\dagger}$ & $\cO(1)^{\dagger\dagger}$   	& \cmark & Partial       & Bounded gradient dissimilarity   & Strongly convex  \\ \hline
FedAvg/N-FedAvg                 & $\cO(\frac{1}{KT})$ & $\cO(N^{-1/2}T^{1/2})^{\ddagger}$ & \cmark	 & Partial       & Bounded gradient             & Strongly convex  \\\hline\hline
FedAvg\cite{khaled2020tighter}  & $\cO(\frac{1}{\sqrt{NT}})$ & $\cO(N^{-3/2}T^{1/2})$     	    & \cmark& Full        & Bounded gradient             & Convex  \\\hline
FedAvg\cite{koloskova2020unified} & $\cO(\frac{1}{\sqrt{NT}})$ & $\cO(N^{-3/4}T^{1/4})$    & \cmark & Full       & Bounded gradient             &  Convex  \\ \hline
FedAvg\cite{karimireddy2019scaffold} & $\cO(\frac{1}{\sqrt{NT}})^{\dagger\dagger}$ & $\cO(1)^{\dagger\dagger}$  & \cmark & Partial       & Bounded gradient dissimilarity   &  Convex  \\ \hline
FedAvg/N-FedAvg      & $\cO\left(\frac{1}{\sqrt{KT}}\right)$ & $\cO(N^{-3/4}T^{1/4})^{\ddagger}$& \cmark			& Partial     & Bounded gradient            &  Convex   \\ \hline\hline
FedAvg & $\cO\left(\exp(-\frac{NT}{E\kappa_1})\right)$ & $ \cO(T^{\beta})$                   & \cmark&  Partial     & Bounded gradient    & Overparameterized LR\\ \hline
FedMass & $\cO\left(\exp(-\frac{NT}{E\sqrt{\kappa_1\tilde{\kappa}}})\right)$ & $ \cO(T^{\beta})$ & \cmark &  Partial     & Bounded gradient    & Overparameterized LR \\ \hline
\end{tabular}
}
\caption{A high-level summary of the convergence results in this paper compared to prior state-of-the-art FL algorithms. This table only highlights the
dependence on $T$ (number of iterations), $E$ (the maximal number of local steps), $N$ (the total number of devices), and $K\leq N$ the number of participated devices. 
$\kappa$ is the condition number of the system and $\beta \in (0,1)$. We denote Nesterov accelerated FedAvg as N-FedAvg in this table.}
{\raggedright 
         $^{\dagger}$ This $E$ is obtained under i.i.d. setting. \\
         $^{\ddagger}$ This $E$ is obtained under full participation setting. \\ 
         % $^{\ddagger}$ The convergence of FedAvg for general overparameterized strongly convex and overparameterized linear regression share the same order in terms of $E, T, N$.\\
         $^{\mathsection}$ In~\cite{haddadpour2019convergence}, the convergence rate is for non-convex smooth problems with PL condition, which also applies to strongly convex problems. Therefore, we compare it with our strongly convex results here.\\
         $^{\ddagger\ddagger}$ The bounded gradient diversity assumption is not applicable for general heterogeneous data when converging to arbitrarily small $\epsilon$-accuracy (see discussions in Sec~\ref{sec:app:comparison}).\\
         $^{\dagger\dagger}$ Although the results in~\cite{karimireddy2019scaffold} is applicable for partial participation setting, their results only achieve linear speedup under full participation setting $K=N$ while we show linear speedup convergence for $K\leq N$ (see discussions in Sec~\ref{sec:app:comparison}). Under partial participation, the communication complexity is $\cO(1)$.)
           \par}
\label{tb:convergenceratev3}
\end{table}

>>>>

\begin{table}[h!]
\hspace{-4em}
{
\centering
\tiny
\begin{tabular}{|c|c|c|c|c|c|c|c|}
\hline Reference                 & Convergence rate    & E                           			& NonIID & Participation & Extra Assumptions  		  & Setting  \\ \hline\hline 
FedAvg\cite{li2019convergence}         & $\cO(\frac{E^2}{T})$& $\cO(1)$                    		& \cmark & Partial       & Bounded gradient   		  & Strongly convex  \\ \hline
FedAvg\cite{haddadpour2019convergence} & $\cO(\frac{1}{KT})$ & $\cO(K^{-1/3}T^{2/3})^{\dagger}$ & \cmark$^{\ddagger\ddagger}$ & Partial       & Bounded gradient diversity   & Strongly convex$^{\mathsection}$  \\ \hline
FedAvg\cite{koloskova2020unified} & $\cO(\frac{1}{NT})$ & $\cO(N^{-1/2}T^{1/2})$     	& \cmark & Full       & Bounded gradient   & Strongly convex  \\ \hline
FedAvg\cite{karimireddy2019scaffold} & $\cO(\frac{1}{NT})^{\dagger\dagger}$ & $\cO(N^{-1/2}T^{1/2})^{\dagger\dagger}$   	& \cmark & Partial       & Bounded gradient dissimilarity   & Strongly convex  \\ \hline
FedAvg/N-FedAvg                 & $\cO(\frac{1}{KT})$ & $\cO(N^{-1/2}T^{1/2})^{\ddagger}$ & \cmark	 & Partial       & Bounded gradient             & Strongly convex  \\\hline\hline
FedAvg\cite{khaled2020tighter}  & $\cO(\frac{1}{\sqrt{NT}})$ & $\cO(N^{-3/2}T^{1/2})$     	    & \cmark& Full        & Bounded gradient             & Convex  \\\hline
FedAvg\cite{koloskova2020unified} & $\cO(\frac{1}{\sqrt{NT}})$ & $\cO(N^{-3/4}T^{1/4})$    & \cmark & Full       & Bounded gradient             &  Convex  \\ \hline
FedAvg\cite{karimireddy2019scaffold} & $\cO(\frac{1}{\sqrt{NT}})^{\dagger\dagger}$ & $\cO(N^{-3/4}T^{1/4})^{\dagger\dagger}$  & \cmark & Partial       & Bounded gradient dissimilarity   &  Convex  \\ \hline
FedAvg/N-FedAvg      & $\cO\left(\frac{1}{\sqrt{KT}}\right)$ & $\cO(N^{-3/4}T^{1/4})^{\ddagger}$& \cmark			& Partial     & Bounded gradient            &  Convex   \\ \hline\hline
FedAvg & $\cO\left(\exp(-\frac{NT}{E\kappa_1})\right)$ & $ \cO(T^{\beta})$                   & \cmark&  Partial     & Bounded gradient    & Overparameterized LR\\ \hline
FedMass & $\cO\left(\exp(-\frac{NT}{E\sqrt{\kappa_1\tilde{\kappa}}})\right)$ & $ \cO(T^{\beta})$ & \cmark &  Partial     & Bounded gradient    & Overparameterized LR \\ \hline
\end{tabular}
}
\caption{A high-level summary of the convergence results in this paper compared to prior state-of-the-art FL algorithms. This table only highlights the
dependence on $T$ (number of iterations), $E$ (the maximal number of local steps), $N$ (the total number of devices), and $K\leq N$ the number of participated devices. 
$\kappa$ is the condition number of the system and $\beta \in (0,1)$. We denote Nesterov accelerated FedAvg as N-FedAvg in this table.}
{\raggedright 
         $^{\dagger}$ This $E$ is obtained under i.i.d. setting. \\
         $^{\ddagger}$ This $E$ is obtained under full participation setting. \\ 
         % $^{\ddagger}$ The convergence of FedAvg for general overparameterized strongly convex and overparameterized linear regression share the same order in terms of $E, T, N$.\\
         $^{\mathsection}$ In~\cite{haddadpour2019convergence}, the convergence rate is for non-convex smooth problems with PL condition, which also applies to strongly convex problems. Therefore, we compare it with our strongly convex results here.\\
         $^{\ddagger\ddagger}$ The bounded gradient diversity assumption is not applicable for general heterogeneous data when converging to arbitrarily small $\epsilon$-accuracy (see discussions in Sec~\ref{sec:app:comparison}).\\
         $^{\dagger\dagger}$ Although the results in~\cite{karimireddy2019scaffold} is applicable for partial participation setting, their results only achieve linear speedup under full participation setting $K=N$ while we show linear speedup convergence for $K\leq N$ (see discussions in Sec~\ref{sec:app:comparison}). The $E$ in the table is obtained under full participation. Under partial participation, the communication complexity is $E=\cO(1)$.
           \par}
\label{tb:convergenceratev3}
\end{table}
